---
title: "ML Mastery with R"
output: html_notebook
---

Spot-Check Machine Learning Algorithms

*Linear Algorithms*
- Methods that make large assumptions about the form of the function being modeled
- high bias but are often fast to train; final models often easy to interpret


- Linear Regression; using the package and function
```{r}
library(mlbench)
data("BostonHousing")

fit <- lm(medv~., BostonHousing)
fit
```
```{r}
predictions <- predict(fit, BostonHousing)
#Summarize the accuracy; mean standard error
mse <- mean((BostonHousing$medv - predictions)^2)
mse
```

- Linear Regression; caret
```{r}
library(caret)
library(mlbench)
data("BostonHousing")

fitControl <- trainControl(method="cv", number=5)
fitLm <- train(medv~., data = BostonHousing,
             method = "lm", metric = "RMSE", 
             preProcess=c("center", "scale"), trControl = fitControl)
fitLm
```

- Logistic Regression; package and function
        - Can be configured to perform a logistic regression suitable for binary 
        classification problems
        - Logistic regression is useful when predicting binary outcomes from a set of 
        continuous predictor variables; frequently preferred over LDA
```{r}
data("PimaIndiansDiabetes")
fit <- glm(diabetes ~., data=PimaIndiansDiabetes, family=binomial(link = 'logit'))
fit
```
```{r}
probabilities <- predict(fit, PimaIndiansDiabetes[,1:8], type = "response")
predictions <- ifelse(probabilities > 0.5, 'pos', 'neg')
#summarize accuracy of model
table(predictions, PimaIndiansDiabetes$diabetes)
```

- Logistic Regression; caret
```{r}
library(caret)
library(mlbench)
data("PimaIndiansDiabetes")

set.seed(7)
fitControl <- trainControl(method = "cv", number = 5)
fitGlm <- train(diabetes~., data=PimaIndiansDiabetes,
                method = "glm", metric = "Accuracy", 
                preProcess=c("center", "scale"), trControl = fitControl)
fitGlm
```





- Linear Discriminant Analysis (LDA); package and function

```{r}
library(MASS)
library(mlbench)
data("PimaIndiansDiabetes")

fit <- lda(diabetes~., data=PimaIndiansDiabetes)
fit
```






- Linear Discriminant Analysis; caret
```{r}
set.seed(7)
fitControl <- trainControl(method = "cv", number = 5)
fitLda <- train(diabetes~., data=PimaIndiansDiabetes,
                method = "lda", metric = "Accuracy",
                preProcess = c("center", "scale"), trControl = fitControl)
fitLda
```

- Regularized Regression; package and function
        - the glmnet() function is in the glmnet package; can be used for classification
        or regression
        
        
- Regularized Regression: Classification Example:
        
```{r}
library(glmnet)
x <- as.matrix(PimaIndiansDiabetes[,1:8])
y <- as.matrix(PimaIndiansDiabetes[,9])

fit <- glmnet(x, y, family = "binomial", alpha = 0.5, lambda = 0.001)
fit
```
```{r}
predictions <- predict(fit, x, type="class")
table(predictions, PimaIndiansDiabetes$diabetes)
```

- Regularized Regrssion: Regression example
```{r}
library(glmnet)
data("BostonHousing")
BostonHousing$chas <- as.numeric(as.character(BostonHousing$chas))

x <- as.matrix(BostonHousing[,1:13])
y <- as.matrix(BostonHousing[,14])
fit <- glmnet(x, y, family = "gaussian", alpha = 0.5, lambda = 0.001)
fit
```
```{r}
predictions <- predict(fit, x, type = "link")
mse <- mean((y-predictions)^2)
mse
```



- Regularized Regression: Classification with Caret

```{r}
library(glmnet)
data("PimaIndiansDiabetes")
set.seed(7)
fitControl <- trainControl(method = "cv", number = 5)
fitGlmnet <- train(diabetes~., data = PimaIndiansDiabetes,
                   method = "glmnet", metric = "Accuracy",
                   preProcess = c("center", "scale"), trControl = fitControl)
fitGlmnet
```

- Regularized Regression: regression with caret and glmnet

```{r}
library(mlbench)
library(glmnet)
data("BostonHousing")

fitControl <- trainControl(method = "cv", number = 5)
set.seed(7)
fitGlmnet <- train(medv~., data = BostonHousing,
                   method = "glmnet", metric = "RMSE",
                   preProcess = c("center", "scale"), trControl = fitControl)
fitGlmnet

```

- Regularized Regression: Regression Example with Caret & glmnet

```{r}
library(mlbench)
library(glmnet)
data("BostonHousing")

fitControl <- trainControl(method = "cv", number = 5)
set.seed(7)
fitGlmnet <- train(medv ~., data = BostonHousing,
                   method = "glmnet", metric = "RMSE",
                   preProcess = c("center", "scale"), trControl = fitControl)
fitGlmnet
```

