---
title: "ML Master with R"
output: html_notebook
---

Chapter 5

Loading in datasets:


*Iris Data*

- Description: Predict iris flower species from flower measurements.   
- Type: Multiclass classification.
- Dimensions: 150 instances, 5 attributes.
- Inputs: Numeric.
- Output: Categorical, 3 class labels.

```{r}
data(iris)
head(iris)
```

*Longley's Economic Regression Data*

- Description: Predict number of people employed from economic variables.   
- Type: Regression.
- Dimensions: 16 instances, 7 attributes.
- Inputs: Numeric.
- Output: Numeric.

```{r}
data(longley)
head(longley)
```

*mlbench Package*
```{r}
install.packages("mlbench")
library(mlbench)
```

*Boston Housing Data*

- Description: Predict the median house price in 1000 for suburbs in Boston.   
- Type: Regression.
- Dimensions: 506 instances, 14 attributes.
- Inputs: Numeric.
- Output: Numeric.

```{r}
data("BostonHousing")
head(BostonHousing)
```

*Wisconsin Breast Cancer Database*

- Description: Predict whether a tissue sample is malignant or benign given properties about the tissue sample.
- Type: Binary Classification.
- Dimensions: 699 instances, 11 attributes.
- Inputs: Integer (Nominal).
- Output: Categorical, 2 class labels.

```{r}
data("BreastCancer")
head(BreastCancer)
```

*Glass Identification Database*

- Description: Predict the glass type from chemical properties.   
- Type: Regression.
- Dimensions: 214 instances, 10 attributes.
- Inputs: Numeric.
- Output: Categorical, 7 class labels.

```{r}
data("Glass")
head(Glass)
```

*Johns Hopkins University Ionosphere database*

- Description: Predict high-energy structures in the atmosphere from antenna data.   
- Type: Regression.
- Dimensions: 351 instances, 35 attributes.
- Inputs: Numeric.
- Output: Categorical, 2 class labels.

```{r}
data("Ionosphere")
head(Ionosphere)
```

*Pima Indians Diabetes Database*

- Description: Predict the onset of diabetes in female Pima Indians from medical record data.
- Type: Binary Classification.
- Dimensions: 768 instances, 9 attributes.
- Inputs: Numeric.
- Output: Categorical, 2 class labels.

```{r}
data("PimaIndiansDiabetes")
head(PimaIndiansDiabetes)
```

*Sonar, Mines, vs. Rocks Dataset*

- Description: Predict metal or rock returns from sonar return data.
- Type: Binary Classification.
- Dimensions: 208 instances, 61 attributes.
- Inputs: Numeric.
- Output: Categorical, 2 class labels.

```{r}
data("Sonar")
head(Sonar)
```

*Soybean Database*

- Description: Predict problems with soybean crops from crop data.
- Type: Multiclass Classification.
- Dimensions: 683 instances, 26 attributes.
- Inputs: Integer (Nominal).
- Output: Categorical, 19 class labels.

```{r}
data("Soybean")
head(Soybean)
```

~ Package: AppliedPredictiveModeling

*Abalone Data*

- Description: Predict abalone age from abalone measurement data.   
- Type: Regression.
- Dimensions: 4177 instances, 9 attributes.
- Inputs: Numerical and categorical.
- Output: Integer.

