---
title: "ML Mastery with R - Chapter 8"
output: html_notebook
---

Visualizing Data

*Univariate Visualization*

- Histograms

```{r}
par(mfrow=c(1,4))
for(i in 1:4){
        hist(iris[,i], main = names(iris)[i], xlab = names(iris)[i])
}
```

- Density Plots
        - these are useful for a more abstract depiction of distribution of each variable
```{r}
library(lattice)
par(mfrow=c(2,2))
for(i in 1:4){
        plot(density(iris[,i]), main=names(iris)[i])
}
```

- Box and Whisker Plots
        - look at the distribution of the data based on quarlitile statistics
        - dots that site outside the whiskeys can be good candidates for outliers
        
```{r}
par(mfrow=c(1,4))
for(i in 1:4){
        boxplot(iris[,i], main = names(iris)[i])
}
```

- Bar plots
        - For datasets with categorical rather than numeric attributes, bar plots can give
        a proportion of instances that belong to each category
        
```{r}
par(mfrow = c(2,4))
for(i in 2:9){
        counts <- table(BreastCancer[,i])
        name <- names(BreastCancer)[i]
        barplot(counts, main=name)
}
```

- Missing Plot
        - Missing data can have big impact on modeling
        - Some techniques ignore missing data, others break
        - You can use a missing plot to get an idea of the amount of missing data in the 
        set; from the Amelia package
        - X axis shows attributes, Y axis shows instances
        - Horizontal lines indicate missing data for an instance
        - Verical blocks represent missing ta for an attribute
        
```{r}
library(Amelia)
library(mlbench)
data("Soybean")

missmap(Soybean, col=c("black", "grey"), legend = FALSE)
```


*Multivariate Visualization*

- Correlation Plot
        - Calculate the correlation between each pair of numeric attributes
```{r}
library(corrplot)
correlations <- cor(iris[,1:4])
corrplot(correlations, method = "circle")
```

- Scatter Plot Matrix
        - Plots two variables agianst each other, with points showing the interaction

```{r}
pairs(iris)
```

- Scatter plot Matrix by Class
        - Points in scatter plot matrix can be colored by class label in classification
        - This can help to spot clear or unclear separation of classes and give an idea
        to the difficult of the problem
        
```{r}
pairs(Species ~., data = iris, col=iris$Species)
```

- Density Plots by Class
        - review the density distirbution of each attribute broken down by class value
        - density can help see separation of classes

```{r}
library(caret)
x <- iris[,1:4]
y <- iris[,5]
scales <- list(x = list(relation="free"), y = list(relation="free"))
featurePlot(x, y, plot="density", scales=scales)
```

- Box and Whisker plots by Class
        - Review boxplot distribution of attributes by class value
        
```{r}
featurePlot(x, y, plot="box")
```

