---
title: "ML Mastery with R"
output: html_notebook
---

Preparing Data for ML with Pre-Processing

*Summary of Transform Methods*
- BoxCox: apply a Box-Cox transform, values must be non-zero and positive.
- YeoJohnson: apply a Yeo-Johnson transform, like a BoxCox, but values can be negative.
- expoTrans: apply a power transform like BoxCox and YeoJohnson.
- zv: remove attributes with a zero variance (all the same value).
- nzv: remove attributes with a near zero variance (close to the same value).
- center: subtract mean from values.
- scale: divide values by standard deviation.
- range: normalize values.
- pca: transform data to the principal components.
- ica: transform data to the independent components. 
- spatialSign: project data onto a unit circle.



*Scale Data*
- Scale transform calculates the standard deviation for an attribute and divides each value by the standard deviation
- Useful operation for scaling data with a gaussian distribution

```{r}
summary(iris[,1:4])
```
```{r}
#Calculate the pre-process paramters from the dataset
preprocessParams <- preProcess(iris[,1:4], method=c("scale"))
preprocessParams
```
```{r}
#Transform the dataset using the parameters
transformed <- predict(preprocessParams, iris[,1:4])
summary(transformed)
```

*Center Data*
- center transform calculates the mean for an attribute and subtracts it from each value

```{r}
preprocessParams <- preProcess(iris[,1:4], method=c("center"))
transformed <- predict(preprocessParams, iris[,1:4])
summary(transformed)
```

*Standardize Data*
- Combination of the scale and center transformation to standardize data
- Attributes will have a mean value of 0 and a standard deviations of 1
```{r}
preprocessParams <- preProcess(iris[,1:4], method = c("center", "scale"))
transformed <- predict(preprocessParams, iris[,1:4])
summary(transformed)
```

*Normalize Data*
- Data values can be scaled into the range of [0,1] - called normalization
```{r}
preprocessParams <- preProcess(iris[,1:4], method = c("range"))
transformed <- predict(preprocessParams, iris[,1:4])
summary(transformed)
```



*Box Cox Transform*
- When an attribute has a gaussian-like distribution but is shifted, this is called a skew
- The distirbtion of an atribute can be shifted to reduce the skew and make it more Gaussian
- BoxCox transform can perform this operation(assumes all values are positive)
- Notice in the example that the only applied transformations were to attributes with skew

```{r}
skew <- apply(PimaIndiansDiabetes[,1:8], 2, skewness)
print(skew)
```

```{r}
summary(PimaIndiansDiabetes[,7:8])
```
```{r}
preprocessParams <- preProcess(PimaIndiansDiabetes[,7:8], method = c("BoxCox"))
transformed <- predict(preprocessParams, PimaIndiansDiabetes[,7:8])
summary(transformed)
```



*Yeo-Johnson Transform*
- Like the Box-Cox but supports raw values that are equal to zero and negative

```{r}
summary(PimaIndiansDiabetes[,7:8])
```
```{r}
data("PimaIndiansDiabetes")
preprocessParams <- preProcess(PimaIndiansDiabetes[,7:8], method = c("YeoJohnson"))
transform <- predict(preprocessParams, PimaIndiansDiabetes[,7:8])
summary(transform)
```



*Principal Component Analysis (PCA) Transform*
- PCA transforms the data to return only the principal compoenets, a technique from multivariate statistics and linear algebra
- The transform keeps those compoenents above the variance threshold (default = .95) or the number to be specificed (pcaComp)
- result are attribtues that are uncorrelated, useful for algorithsm like linear and genearlized linear regression

```{r}
data(iris)
summary(iris)
```
```{r}
preprocessParams <- preProcess(iris, method=c("center", "scale", "pca"))
transformed <- predict(preprocessParams, iris)
summary(transformed)
```

*Independent Component Analysis (ICA) Transform*

```{r}
data("PimaIndiansDiabetes")
summary(PimaIndiansDiabetes[,1:8])
```
```{r}
preprocessParams <- preProcess(PimaIndiansDiabetes[,1:8], 
                               method = c("center", "scale", "ica"), n.comp=5)
transformed <- predict(preprocessParams, PimaIndiansDiabetes[,1:8])
summary(transformed)
```

